\documentclass{beamer}
\mode<presentation>
{
    \usetheme{Copenhagen} 
    \usecolortheme{beaver}
}

\AtBeginSection[]
{
    \begin{frame}{Table of Contents}
        \tableofcontents[currentsection]
    \end{frame}
}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{hyperref}

\author{Anon Ymous}
\date{\today}

\title{Beamer slides}

\begin{document}

\section{Beamer structure}
\subsection{Sections and Subsections}

\begin{frame}[fragile]
    \frametitle{Sections and subsections}
    \framesubtitle{Structuring frames}

    Sections and subsections help organize and structure your presentation:
    \begin{enumerate}
        \item<1-| alert@1>
        \verb`\section[Short Section Name]{Long Section Name}`
        \item<1-| alert@2>
        \verb`\subsection[Short Section Name]{Long Section Name}`
    \end{enumerate}
    \vfill
    ``Short names'' go into slide headers; and ``Long names'' go into outlines.
    \vfill
\end{frame}
\begin{frame}[fragile]
    \frametitle{Tips and tricks}
    \framesubtitle{Structuring Tips and Tricks}
    \begin{itemize}
        \item<1-| alert@1>
        The sections and subsections will appear automatically in the
        presentation's outline.
        \item<1-| alert@2>
        Use \verb`\tableofcontents[section]` to keep audience informed of
        your talk's general plan.
    \end{itemize}
\end{frame}
\begin{frame}[fragile]
    \frametitle{AtBeginSection}
    \framesubtitle{A presentational trick}

    Insert the following in the preamble:
    \begin{verbatim}
    \AtBeginSection[]
    {
        \begin{frame}{Table of Contents}
            \tableofcontents[currentsection]
        \end{frame}
    }
    \end{verbatim}

    You'll have at the beginning of every section an automatically inserted
    section outline, helping your audience to stay informed of progress.
\end{frame}

\subsection{Structuring guideline}

\begin{frame}
    \frametitle{Structuring numbers}
    \begin{description}
        \item<1-| alert@1>[presentation] ideally 3 sections, but not more then 4.
        \item<1-| alert@2>[sections] ideally 3 subsections, but not more then 4.
        \item<1-| alert@3>[sections] ideally have the same number of subsections.
        \item<1-| alert@4>[subsections] ideally contain in average 7 frames,
        but not more then 15.
    \end{description}
\end{frame}
\begin{frame}
    \frametitle{Tip on displayed content}

    According to cognitive science studies, the human mind captures in
    average 4 concepts from a presentation slide, so this presentation is most
    probably a bad one in regard to this rule.
\end{frame}

\section{Beamer themes}
\subsection{Theme structure}
\begin{frame}
    \frametitle{Color themes, Inner themes, and Outer themes}
    \framesubtitle{What presentation themes are made of}
    \begin{description}
        \item<1-| alert@1>[Color themes]
        controls colors for bullets, background, text, etc.
        \item<1-| alert@2>[Fonts themes]
        controls which fonts or font attributes are used. Font colors of all
        text elements can be specified independently.
        \item<1-| alert@3>[Inner themes]
        controls main title, environments, figures and tables, footnotes, etc.
        \item<1-| alert@4>[Outer themes]
        control head-/foot-lines, sidebars, frame titles, etc.
    \end{description}
\end{frame}

\begin{frame}[fragile]
    \frametitle{Theme list}
    \framesubtitle{Some commonly used themes}

    default, AnnArbor, Antibes, Bergen, Berkeley, Berlin, Boadilla,
    CambridgeUS, Copenhagen, Darmstadt, Dresden, Frankfurt, Goettingen,
    Hannover, Ilmenau, JuanLesPins, Luebeck, Madrid, Malmoe, Marburg,
    Montpellier, PaloAlto, Pittsburgh, Rochester, Singapore, Szeged, Warsaw.

    \vfill

    Setting theme: \verb`\usetheme{theme name}`
\end{frame}
\begin{frame}[fragile]
    \frametitle{Color themes list}
    \framesubtitle{Some commonly used color themes}

    default, albatross, beaver, beetle, crane, dolphin, dove, fly, lily,
    orchid, rose, seagull, seahorse, whale, wolverine.

    \vfill

    Setting color theme: \verb`\usecolortheme{colorthemename}`
\end{frame}
\begin{frame}[fragile]
    \frametitle{Font themes list}
    \framesubtitle{Some commonly used fonts themes}

    default, professionalfonts, serif, structurebold, structureitalicserif,
    structuresmallcapsserif, structureitalicserif

    \vfill

    Setting font themes: \verb`\usefonttheme{fontthemename}`
\end{frame}
\begin{frame}[fragile]
    \frametitle{Inner themes list}
    \framesubtitle{Some commonly used inner themes}

    circles, inmargin, rectangles, and rounded

    \vfill

    Setting inner themes: \verb`\useinnertheme{innerthemename}`
\end{frame}
\begin{frame}[fragile]
    \frametitle{Outer themes list}
    \framesubtitle{Some commonly used outer themes}

    default, infolines, miniframes, smoothbars, sidebar, split, shadow, tree,
    smoothtree.

    \vfill

    Setting outer themes: \verb`\useoutertheme{outerthemename}`
\end{frame}


\end{document}
